---
title: "PRNFTP with latent variable adjustment"
author: "Justine Drouault (INRAE)"
date: "2025-07-04 [v1.1]"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

#### This script reproduces the PRN-FTP model shown in Fig. 3 of the paper. #### 
#### In this script, Tt and GDD interchangeably refer to thermal time calculated with Eq. S2 in the paper #### 

```{r setup, include=FALSE}
## clear objects in memory
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

#### Load the required packages ####

```{r}
library(tidyverse)
library(nasapower) ### to get the environmental conditions (temperature, but you can get others)
library(TrenchR) ### to get the daylength 
library(chngpt) ### to fit the change point model and get the prn-ftp
```

#### Define paths ####

```{r}
whose_dir <- "~/user_path"
data_path <- paste0(whose_dir, "/data_path/")
functions_path <- paste0(whose_dir, "/functions_path/")
outputs_path <- paste0(whose_dir, "/outputs_path/")

```

#### Load functions ####

```{r,}
## this function computes the thermal time (Tt) from hourly temp data 
source(paste0(functions_path,"WangEngel.R"))

### this function sums Tt between starting date (e.g planting or emergence) until a threshold of Tt (e.g BVP_ti), and returns the date of year at which the threshold is reached 
Date_TI <- source(paste0(functions_path,"Functions.R"))

### this function sums Tt between between two dates (e.g planting or emergence and anthesis), returning a value of accumulated Tt 
GDD_cum_date <- source(paste0(functions_path,"Functions.R"))

### this function gets the daylength for a given location and day of the year, using the DOY value and the coordinates of the sites 
daylength_ti <- source(paste0(functions_path,"Functions.R"))

```

#### Construct the x-axis for the PRN-FTP (the photoperiod index, DLs) ####

###### Step 1: Calculate BVP-Ti per genotype ######

<!-- BVP_Ti = (Ptip/(alphaphyll/plast))*(LF-Lpri_em) -->
<!-- BVP_Ti = thermal time from emergence to tassel inititation  -->
<!-- Ptip = phyllochron, visible leaves  -->
<!-- alphaphyll/plast = ratio between plastochron and phyllochron -> cst = 1.173 -->
<!-- FLN or LF = final leaf number  -->
<!-- Lpri_em = number of primordium formed at emergence -> cst = 5.5 -->

```{r}
# retrieve BLUEs for final leaf number and phyllochron
file_s2 <- read.delim(paste0(data_path, "File_S2.txt"), header=T, sep = "\t")

panel1 <- file_s2 %>%
  dplyr::group_by(genotype) %>% ## apply the formula per genotype 
  dplyr::mutate(TTem_ti= ifelse(!is.na(BLUE_Ptip) & !is.na(BLUE_FLN), (BLUE_Ptip/1.73)*(BLUE_FLN - 5.5), NA ),
                TTem_ti = round(TTem_ti, 2)) %>% 
  as.data.frame()

# if you do not have values of phyllochron or FLN use the reference of BVP_ti used in the paper 326 gdd units
```

The chunks containing step 2 and step 3 are here as an example to show how hourly temperature data can be extracted from nasapower and transformed in Tt. But, as in our study a mix of station and satellite data were used (see File S3), we provided at the end of step 3 the file containing the Tt calculated for each environment (whether it is station or satellite). This file we be used in the rest of the script.

###### Step 2: Retrieve hourly temperature data per for each environment ######

Here we get hourly temperature data per env (year*location) to compute the Tt, based on Eq. S2 in the paper.
If you have station data you need to get hourly temperature data to run the Tt function used here.

```{r}
# load field information used in the study
file_S4 <- read.delim(paste0(data_path, "File_S4_inputdata.txt"), header=T,  sep="\t")

coordinates <- file_S4 %>%
  dplyr::select(lat, lon, env, year, project) %>% ### extract the coordinates and year of your file
  dplyr::distinct() 

# use nasapower to get the temperature data
meteo_data_hourly <- do.call(rbind, lapply(split(coordinates,as.factor(coordinates$env)), function(x)
{
  daily_single_ag <- get_power(
    community = "ag",
    lonlat = c(x$lon, x$lat), ## specify the coordinate of the env
    pars = c("T2M"), ### get the env parameters you want, you can hack on nasapower website 
    dates = c(paste0(x$year,"-01-01"),paste0(x$year,"-12-31")), ## get the temperature values for the year corresponding to the env 
    temporal_api = "hourly") ### need hourly temperature data 
  daily_single_ag$env <- unique(x$env) ### Add the environments to the meteo file because nasapower does not keep it
  daily_single_ag$project <- unique(x$project) ### Add the project to the meteo file because nasapower does not keep it
  return(daily_single_ag)}))
```

###### Step 3: Compute Tt per hour per day per environment ######
 
```{r}
meteo_data_hourly_1 <- meteo_data_hourly %>%
  dplyr::group_by(LAT, YEAR, MO, DY) %>%
  dplyr::mutate(WangEngel = .rowMeans(WangEngel(hTemp = T2M, n=24), n=24, 1)) %>% ## Get WangEngel GDD by lat and date
  dplyr::ungroup()%>%
  dplyr::select(env, project, LON, LAT, YEAR, MO, DY, WangEngel) %>% 
  dplyr::rename("MM" = MO, "DD" = DY) %>%
  dplyr::distinct() %>%
  tidyr::unite(YYYYMMDD, c(YEAR:DD),sep = "_", remove = F) %>%
  dplyr::mutate(YYYYMMDD = as.Date(YYYYMMDD, format = "%Y_%m_%d"))  %>%
  dplyr::mutate(YYYYMMDD = as.character(YYYYMMDD)) %>%
  as.data.frame


# File with the thermal time for all the environments whether the meteo data come from station or satellite
meteo_data_hourly_out_git <- read.csv(paste0(data_path, "20240624GitHub_meteo_data.csv"), header = T) %>%
  split(.$LAT) %>%
  map(function(x) x %>% filter(!is.na(MO) | !is.na(DY))) %>% bind_rows() 
```

###### Step 4: Get DLs ######

<!-- The required values to get the daylength experienced at BVP-ti (Dls) are : -->
<!-- - The coordinates of your sites -->
<!-- - The temperature of each of your sites -->
<!-- - The plating date -->
<!-- - The emergence date -->

<!-- We use the file containing the planting date and emergence date, coordinates of the field, genotype-specific values for BVP-ti (if available) or a common reference value (320) for BVP_ti-->

```{r,}
# for this example we don't work with the entire panel, but only with a subset of genotypes (Fig 3 in the paper)
panel1 <- panel1 %>%
  dplyr::filter(genotype %in% unique(file_S4$genotype)) 

# use the functions Date_TI and daylength_ti, loaded above to get the date_DLs and daylength_DLs
x_axis_constructed <- file_S4 %>%
   dplyr::select(country, loc, year, env, lat, lon, genotype, project, date_planted, date_emerged) %>% #loc,
  dplyr::full_join(panel1) %>% ## merge to get BVP_ti 
  dplyr::mutate(across(c(date_planted, date_emerged), ~as.Date(., format = "%m/%d/%y")), ## here the date format may needs to be adjusted according to the format you have in the used file
                across(c(date_planted,  date_emerged, lat),~as.character(.))) %>% ## need to be in character to match the meteo file and be read by the functions 
  dplyr::group_by(env, genotype, project, lat) %>% ## !! here go per row, or env & genotype to not get mixed data 
  dplyr::mutate(date_DLs= ifelse(is.na(TTem_ti) | is.na(date_emerged), NA, Date_TI(dataset =  meteo_data_hourly_out_git, # or meteo_data_hourly_1 ,  
                                                                                   LAT1= unique(lat), ENV1 = unique(env), 
              start = unique(date_emerged), threshold = TTem_ti, #326
              DATE = "YYYYMMDD", GDD ="WangEngel")), ### use ind thermal time at TI to get the date of the year at TI 
              date_DLs = as.character(date_DLs), 
              doy_DLs = lubridate::yday(date_DLs),
              lat = as.numeric(as.character(lat)), 
              daylength_DLs = ifelse(!is.na(doy_DLs), Daylength(lat, doy_DLs), NA), 
              lat = as.character(lat))
```

#### Construct the y-axis for the PRN-FTP (accumulated Tt to anthesis) ####

###### Step 1: Compute Tt from emergence to anthesis ######

```{r}
# Get Tt to anthesis by summing Tt from emergence to date anthesis
y_axis_constructed <- file_S4 %>%
  # dplyr::filter(env != "2005_NC") %>%
  dplyr::select(country, loc,  year, env, lat, lon, genotype, project, date_planted, date_emerged, BLUE_DTA, SE_DTA) %>%
  dplyr::mutate(across(c(date_planted, date_emerged), ~as.Date(., format = "%m/%d/%y")), ## here the date format may needs to be adjusted according to the format you have in the used file #~as.Date(., format = "%m/%d/%y"))
    blue_date_dta = (date_planted + BLUE_DTA), across(c(date_planted,  date_emerged, blue_date_dta, lat),~as.character(.))) %>%
  # dplyr::rowwise() %>%
  dplyr::group_by(env, genotype, project) %>%
  # calculation Tt emergence - dta 
  dplyr::mutate(blue_dta_eqs2 = ifelse(!is.na(blue_date_dta), 
                                     GDD_cum_date(dataset = meteo_data_hourly_out_git, # or meteo_data_hourly_1
                                                  LAT1 = unique(lat), ENV1 = unique(env), threshold_max = unique(blue_date_dta), 
                                                  threshold_min = unique(date_planted),
                                                  DATE = "YYYYMMDD", GDD = "WangEngel" ), NA)) %>%
  # calculation Tt planting - dta 
  dplyr::mutate(blue_dta_em_eqs2 = ifelse(!is.na(blue_date_dta), 
                                     GDD_cum_date(dataset = meteo_data_hourly_out_git, # or meteo_data_hourly_1
                                                  LAT1 = unique(lat), ENV1 = unique(env),  threshold_max = unique(blue_date_dta), 
                                                  threshold_min = unique(date_emerged),
                                                  DATE = "YYYYMMDD", GDD = "WangEngel" ), NA))
```

###### Step 2: Adjust for latent variable effects ######

We are going to create two sets of insensitive genotypes, calculate their overall mean, get the deviation of the environmental mean of these genotypes from the overall mean, this deviation will be used to adjust the sensitive genotype for their variation in blue_dta_em_eqs2 due to latent variable. 

set1 = B37, B73, M37W, Mo17, Oh43 for PhotoGrid, MDR, and Panzea environments
set2 = 2369 and LH123Ht for Maize ATLAS environments 

```{r}
### Adjust Tt to anthesis for latent variables

# Get the deviation of insensitive genotypes from their overall mean per environment 
insensitive_genotype <- c("B37", "B73", "M37W", "Mo17", "Oh43", "LH123Ht", "2369") # list of insensitive genotypes

adjustement_values <- y_axis_constructed %>%
  dplyr::filter(genotype %in% insensitive_genotype) %>%
  dplyr::mutate(set = ifelse(project == "Maize ATLAS", "set2", "set1")) %>% ### create sets
  dplyr::mutate(genotype = ifelse(set == "set1" & genotype == "LH123Ht", NA, genotype)) %>%
  dplyr::mutate(genotype = ifelse(set == "set1" & genotype == "2369", NA, genotype)) %>%### remove 2369 and LH123Ht from PhotoGrid environments
  dplyr::filter(!is.na(genotype)) %>%
  dplyr::group_by(set) %>%
  dplyr::mutate(general_mean_dta_em_eqs2 = mean(blue_dta_em_eqs2, na.rm = T)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(env) %>%
  dplyr::mutate(env_mean_dta_em_eqs2 = mean(blue_dta_em_eqs2, na.rm = T)) %>%
  dplyr::ungroup() %>%
  dplyr::rowwise() %>%
  dplyr::mutate(deviation_from_general_mean = env_mean_dta_em_eqs2 - general_mean_dta_em_eqs2) %>%
  dplyr::select(env, deviation_from_general_mean) %>%
  dplyr::distinct()

# Adjust blue_dta_em_eqs2 with the deviation values 

y_axis_constructed <- y_axis_constructed %>%
  dplyr::full_join(adjustement_values) %>%
  dplyr::group_by(env, genotype) %>% # adjustment is done per env 
  dplyr::mutate(blue_dta_em_eqs2_adjusted = blue_dta_em_eqs2 - deviation_from_general_mean) 
```

#### Merge x-axis and y-axis data ####

```{r}
prnft <- x_axis_constructed %>%
  dplyr::full_join(y_axis_constructed)

# code to run if you want to recreate exactely file S4
file_to_save <- prnft %>%
  dplyr::select(-BLUE_Ptip, -BLUE_FLN, -deviation_from_general_mean ) %>%
  dplyr::rename(se_day_dta = SE_DTA, bvpti_platform = TTem_ti) %>%
  dplyr::relocate(date_DLs, .after = blue_dta_em_eqs2_adjusted ) %>%
  dplyr::relocate(doy_DLs, .after = date_DLs ) %>%
  dplyr::relocate(daylength_DLs, .after = doy_DLs ) %>%
  dplyr::relocate(bvpti_platform, .after = date_emerged )

# write.csv(file_to_save, paste0(outputs_path,"File_S4.csv"), row.names = F) 
```

#### PRN-FTP plots ####

```{r,}
## Filter the sensitive genotypes
prnft <- prnft %>%
  dplyr::filter(genotype == "CML10" | genotype == "CML258"| genotype == "CML277"| genotype == "CML341" | genotype == "CML373" | genotype == "Tzi8" | genotype == "Tzi9" ) 

prnft_plot_unadjusted <- prnft %>%
  ggplot(aes(x= daylength_DLs, y = blue_dta_em_eqs2))+ 
  geom_point() +
  facet_wrap(~genotype)
prnft_plot_unadjusted

prnft_plot_adjusted <- prnft %>%
  ggplot(aes(x= daylength_DLs, y = blue_dta_em_eqs2_adjusted))+ 
  geom_point() +
  facet_wrap(~genotype)
prnft_plot_adjusted
```

#### Fit bilinear model with change point to get paramater estimates for the PRN-FTP ####

With a sufficient density of data and coverage of DLs spanning SD and LD environments, photoperiod sensitive genotypes are expected to follow a bilinear pattern of response. In SD environments T_t^(em-ant) remains constant, and above a critical threshold for LD environments it increases linearly with photoperiod. For this, we modeled tthe PRN-FTP can be modeled using as a continuous two-phase (bilinear) regression model function with threshold detection (Fong et al., 2017a).

```{r,}
###### adjusted values 
## lists for storage
Q <- list()
R <- list()
S <- list()
median_loglik <- list()
gtypes <- sort(unique(prnft$genotype)) ### subset per genotype 
out_adjusted <- NULL

## fit model per genotype
for (a in 1:length(gtypes)) {
  # a <- 1
  gtype_sub <- subset(prnft, genotype==gtypes[a]) 
  Q[[a]] <- chngptm(formula.1=blue_dta_em_eqs2_adjusted~1,
                    formula.2=~daylength_DLs, 
                    type="hinge", family="gaussian", 
                    #lb.quantile=0.3, ## if you want to fix the threshold
                    data=gtype_sub) 
  median_loglik[[a]]<- as.data.frame(unclass(summary(Q[[a]]$logliks)), check.names = FALSE,
                                     stringsAsFactors = FALSE)[3,1]
  median_loglik <- median_loglik[[a]]
  
  # Extract intercept, slope, and SEs
  intercept <- Q[[a]]$coefficients[1]
  thershold <- Q[[a]]$coefficients[3]
  slope <- Q[[a]]$coefficients[2]
  intercept_se <- sqrt(diag(vcov(summary(Q[[a]]$best.fit))))[1]
  thershold_se <- summary(Q[[a]])$chngpt['Std. Error']
  slope_se <- sqrt(diag(vcov(summary(Q[[a]]$best.fit))))[2]
  intercept_pvalue <- summary(Q[[a]]$best.fit)$coefficients[1,"Pr(>|t|)"]
  slope_pvalue <- summary(Q[[a]]$best.fit)$coefficients[2,"Pr(>|t|)"]
  
  # Extract the genotype name 
  genotype <- unique(gtype_sub$genotype)
  
  # Get teh fit of the model 
  RSS <- c(crossprod(residuals(Q[[a]])))
  MSE <- RSS / length(residuals(Q[[a]]))
  RMSE <- sqrt(MSE)
  
  # Assemnble the element to make a summary table of the PRN-FTP for each genotype 
  BVP_ti<- as.numeric(unique(gtype_sub$BVP_ti))
  temp <- cbind(genotype, "intercept"=round(intercept,1), "intercept_se"=round(intercept_se,1), "intercept_pvalue"=intercept_pvalue, 
                         "thershold"=round(thershold,1), "thershold_se"=round(thershold_se,1), "median_loglik"=round(median_loglik,1), 
                         "slope"=round(slope,1), "slope_se"=round(slope_se,1), "slope_pvalue"=slope_pvalue, 
                         "BVP_ti"=round(BVP_ti,1), "RMSE" = round(RMSE, 1))
  out_adjusted <- rbind.data.frame(out_adjusted, temp)
}

rownames(out_adjusted) <- 1:nrow(out_adjusted)
out_adjusted

out_adjusted <- out_adjusted %>%
  dplyr::mutate(across(intercept:RMSE, ~ as.numeric(as.character(.))))

```
#### Alternative the bilinear model - fit the linear model ####

When fitting the bilinear model is not feasible due to insufficient density of data, inadequate coverage of 〖DL〗^s for threshold detection, or because it is not an appropriate model for all genotypes (i.e., photoperiod insensitive genotypes), we modeled the PRN-FTP as a linear regression function, forgoing threshold estimation. So that the intercept for T_t^(em-ant) is estimated at the mean 〖DL〗^s of SD environments rather than the shortest day environment, environments across the MET were first classified as SD or LD based on whether 〖DL〗^s falls below or above a fixed threshold, respectively (we used 13.5 h which corresponded to the average threshold estimated from the analysis of Dataset D4, see results). 

## Step 1: Infer the critical photoperiod

# The critical photoperiod is defined as the averaged critical photoperiod of the seven tropical genotypes of dataset D4, when the TTem-ant is adjusted and DLs is genotype specific

prnft <- prnft %>%
  dplyr::mutate(Parameters = ifelse(daylength_DLs < 13.5, "SD", "LD")) 

## Step 2: Calculate the DLs mean in LD and SD

# These values will be used for the adjustement of the linear model were the average daylength in SD will be set to 0
   diff_photoperiod <- prnft %>% 
    dplyr::select(country:project, daylength_DLs, blue_dta_em_eqs2_adjusted, Parameters) %>%
    dplyr::distinct() %>%
    dplyr::group_by(genotype, Parameters) %>%
    dplyr::mutate(genotype = as.character(genotype), 
                  mean_daylength_DLs = mean(daylength_DLs, na.rm =T)) %>%
    dplyr::select(genotype, mean_daylength_DLs, Parameters) %>%
    dplyr::distinct()  
  
   
## Step 3: Extract the DLs mean and adjsuted TTem-ant to fit the linear model 

  fit_for_linear_regression <- prnft %>%
    dplyr::select(genotype, country,env, Parameters, blue_dta_em_eqs2, blue_dta_em_eqs2_adjusted) %>%
    dplyr::distinct() %>%
    dplyr::group_by(genotype, Parameters) %>%
    dplyr::full_join(diff_photoperiod) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(genotype) %>%
    dplyr::mutate(min_daylength = min(mean_daylength_DLs), 
                  new_mean_daylength_bvpti = mean_daylength_DLs - min_daylength)
  
## Step 4: Fit the linear model on each genotype 

  # split the dataset by group
  regression.sp <- split(fit_for_linear_regression, fit_for_linear_regression$genotype)
  
  # run separate `lm` on each group and store the results in a list
  r_corrected <- lapply(regression.sp, function(x) do.call("lm", list(blue_dta_em_eqs2_adjusted ~ new_mean_daylength_bvpti,  data = x)))
  
  # extract the coefficient of target variable in corrected data
  slope <- sapply(r_corrected, function(x)x$coefficients[["new_mean_daylength_bvpti"]])
  intercept <- sapply(r_corrected, function(x)x$coefficients[["(Intercept)"]])
  slope_se <- sapply(r_corrected, function(x)summary(x)$coefficients[,"Std. Error"][["new_mean_daylength_bvpti"]])
  se_intercept <- sapply(r_corrected, function(x)summary(x)$coefficients[,"Std. Error"][["(Intercept)"]])
  pvalue_slope <- sapply(r_corrected, function(x)summary(x)$coefficients[,"Pr(>|t|)"][["new_mean_daylength_bvpti"]])
  pvalue_intercept <- sapply(r_corrected, function(x)summary(x)$coefficients[,"Pr(>|t|)"][["(Intercept)"]])
  
  slope <- as.data.frame(slope)
  intercept <- as.data.frame(intercept)
  slope_se <- as.data.frame(slope_se)
  se_intercept <- as.data.frame(se_intercept)
  pvalue_slope <- as.data.frame(pvalue_slope)
  pvalue_intercept <- as.data.frame(pvalue_intercept)

# Get the fit of the model 
  RMSE_results <- lapply(r_corrected, function(x) {
  RSS <- sum(residuals(x)^2)  # Residual Sum of Squares
  MSE <- RSS / length(residuals(x))  # Mean Squared Error
  RMSE <- sqrt(MSE)  # Root Mean Squared Error
  return(c(RSS = RSS, MSE = MSE, RMSE = RMSE))
})

  RMSE_results <- as.data.frame(RMSE_results)
  
  RMSE_results <- RMSE_results[3,]
  
  RMSE_results <- RMSE_results %>%
    tidyr::pivot_longer(
    everything(), 
    names_to = c("genotype"), 
    values_to = "RMSE"
  )

  ## Create the outcome table  
  
linear_regression_final <- slope %>%
  dplyr::full_join(slope_se) %>%
  dplyr::full_join(pvalue_slope) %>%
  dplyr::full_join(intercept) %>%
  dplyr::full_join(se_intercept) %>%
  dplyr::full_join(pvalue_intercept) %>%
  dplyr::full_join(RMSE_results) %>%
  dplyr::mutate(across(slope:RMSE, ~round(., 2)))

#### Recreate figure 4 ####

```{r,}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

out_adjusted <- out_adjusted %>%
  dplyr::select(genotype, intercept, thershold, slope)

facet_7p <- prnft %>% #data_merge_bis
  dplyr::full_join(out_adjusted) %>%
  dplyr::mutate(loc = factor(loc, levels = c("Gua", "Sen", "PR", "Mex", "FL", "cTX", "GA","nTX", "andrNC", "clayNC", "NC", "DE", "IA","NY", "WI", "Fra"))) %>%
  dplyr::arrange(loc) %>%
  dplyr::arrange(loc) %>%
  ggplot(aes(x = daylength_DLs, y = blue_dta_em_eqs2_adjusted)) +
  geom_point(size=3, alpha=0.8, color="black") + 
  geom_vline(aes(xintercept = thershold), color="#D55E00", size=1.5) +
  geom_segment( aes(x = min(daylength_DLs), y = intercept, xend = thershold, yend = intercept), color="#0072B2", size=1.5) +
  geom_segment(aes(x = thershold, y = intercept, xend = max(daylength_DLs),
                   yend = ( intercept + ( max(daylength_DLs) - thershold) * slope ) ), color="#F0E442", size=1.5) +
  ylim(650, 1300) +
  facet_wrap(vars(genotype), ncol=4, scales = "fixed") +
  xlab(quote(bolditalic(DL)^bold(s) ~ bold("("*h*")"))) +
  ylab(quote(atop(bolditalic(T)[t]^bold(em-ant) ~ bold(" ("*degree*"Cd)"), "(adjusted values)"))) +
  theme(plot.background = element_blank()
        ,legend.position = "none"
        ,legend.direction="vertical"
        ,legend.key.size = unit(1, "cm")
        ,legend.text = element_text(size = 10, face="bold")
        ,aspect.ratio = 1
        ,legend.title = element_text(size=16, face="bold")
        ,title = element_text(size=14, face="bold")
        ,panel.grid.minor = element_blank()
        ,panel.grid.major.x = element_line(colour="grey", size = 0.5, linetype=3)
        ,panel.grid.major.y = element_line(colour="grey", size = 0.5, linetype=3)
        ,panel.border = element_rect(colour="grey", size = 0.5, fill=NA)
        ,panel.background = element_blank()
        ,plot.title = element_text(face="bold")
        ,axis.title.x = element_text(size=18, margin = margin(t=18))
        ,axis.text.x = element_text(size=18, margin = margin(t=11))
        ,axis.title.y = element_text(size=18, margin = margin(r=18))
        ,axis.text.y = element_text(size=18)
        ,axis.ticks.y = element_blank()
        ,axis.ticks.x = element_blank()
        ,strip.text.x = element_text(size = 16, face="bold")
        # top, right, bottom, left
        ,plot.margin=unit(c(0.55,0.5,0.8,0.5), "cm")
  )
facet_7p
```
